Lucy.js: Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex
cleaning up

In this paper, we introduce Lucy.js, a fully client-side JavaScript search engine that is an extension of the current IndexedDB API~\cite{indexeddb}. It has been designed to be easy for anyone currently using IndexedDB in their application to begin indexing and searching full-text content, without needing to modify pre-existing code or move to a new framework or mode of communication. There are also no dependencies on a server or network, so it can be harnessed offline. In our implementation, we created several types of indexes commonly used in well-known search engines, such as Lucene and within PostgreSQL, including inverted indexes, prefix and suffix tries, and variations on these. We discuss how we create these indexes on top of the IndexedDB framework as well as how the different indexes are suited to different tasks. We compare their performance on different types of queries and with different sizes and types of datasets. We find that...FILL IN HERE.

@@

We created Lucy.js in JavaScript, as the IndexedDB API is also a JavaScript API. The code consists of four main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-hybrid.js} *********UPDATE? plus some third-party files that the user must include in their HTML file. The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.

@@

Client-side search engines offer new functionality to client-side applications and potential speed improvements for applications that query a server-side search engine. We implemented a client-side search engine as an extension of the IndexedDB API, building several different types of index structures including inverted indexes, prefix and suffix tries, and a hybrid approach combining the two. We compare the performance of our indexes against each other and find that our hybrid approach is overall the fastest. We additionally evaluate our system by implementing a full-text search bar and a typeahead search bar and compare performance of a client-side only approach with a server-side only approach using MySQL. We find that for small to moderate datasets, the network latency incurred by trips to the server make client-size querying faster. Finally, we imagine potential applications that could be enhanced using our client-side search engine.

>>>>

In this paper, we introduce Lucy.js, a fully client-side JavaScript search engine that is an extension of the current IndexedDB API~\cite{indexeddb}. It has been designed to be easy for anyone currently using IndexedDB in their application to begin indexing and searching full-text content, without needing to modify pre-existing code or move to a new framework or mode of communication. There are also no dependencies on a server or network, so it can be harnessed offline. In our implementation, we created several types of indexes commonly used in well-known search engines, such as Lucene and within PostgreSQL, including inverted indexes, prefix and suffix tries, and variations on these. We discuss how we create these indexes on top of the IndexedDB framework as well as how the different indexes are suited to different tasks. We compare their performance on different types of queries and with different sizes and types of datasets. We find that overall, our hybrid trie index, which is a combination of inverted index and trie, performs the best.

@@

We created Lucy.js in JavaScript, as the IndexedDB API is also a JavaScript API. The code consists of four main files - \texttt{lucy.js}, \texttt{invindex.js}, \texttt{trieindex.js},  and \texttt{trieindex-hybrid.js} plus some third-party files that the user must include in their HTML file. The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.

@@

Client-side search engines offer new functionality to client-side applications and potential speed improvements for applications that query a server-side search engine. We implemented a client-side search engine as an extension of the IndexedDB API, building several different types of index structures including inverted indexes, prefix and suffix tries, and a hybrid approach combining the two. We compare the performance of our indexes against each other and find that our hybrid approach is overall the fastest. We additionally evaluate our system by implementing a full-text search bar and a typeahead search bar and compare performance of a client-side only approach with a server-side only approach using MySQL. We find that for small to moderate datasets, the network latency incurred by trips to the server make client-size querying faster. Finally, we imagine potential applications that could be enhanced or realized using our client-side search engine.
